Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-12-13 Arxiv/main.tex
update main accuracy

By solving following equations:
\begin{itemize}
  \item
\[
\frac{1}{\nomalizer{\dataobs}} = 0.19673467014
\]
we can get the range where we can do better than $\lapmech$ on outputting the correct answer and
\[
\frac{1}{\nomalizer{\dataobs}} = 0.31606027941
\]
we can get the range where we can do better than $\ilapmech$ on outputting the correct answer and

>>>>

By solving following equations:
\begin{itemize}
  \item
\[
\frac{1}{\nomalizer{\dataobs}} = 0.19673467014\ or\ 0.31606027941
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer.
